---
title: "Lecture10a_Lecture"
author: "Amanda"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# If you're asking: What package or function should I use to do this thing?
- Google it (add R software or .R to the end of your search)    
- CRAN Task Views    

# What should you look out for if there is something wrong?  
- red x next to your code will show that there is an error   
- Error (need to fix to run), Warning (will still run), or Message   
- if you do not know how to fix the error message, google it!!   

# Some common errors/issues to keep an eye out for
- Error in _______: could not find function "__________"    
  - this means the function hasn't been attached   
  - maybe misspelled something   
- Error in ____ %>% _____: could not find function "%"%   
  - Make sure you ran the packages!!   
- Error in ________ : object '______' not found    
  - the object hasnt been created or stored   
  - yoube mistyped the object name 
- Warning: Ignoring unknown parameters: ________'
  - use ?_____ to figure out if you spelled everything right
  
# Install Packages
```{r}
install.packages('reprex') #reproducible example
install.packages('datapasta') #copy and paste
install.packages('styler') # copy and paste in style
```

# Let's Practice 
```{r}
library(tidyverse)
mpg %>%
  ggplot(aes(x = displ, y = hwy))%>%
  geom_point(aes(color = class))
```

# Use DataPasta 
```{r}
tibble::tribble(
    ~lat,    ~long, ~star_no,
  33.548, -117.805,      10L,
  35.534, -121.083,       1L,
  39.503, -123.743,      25L,
  32.863,  -117.24,      22L,
   33.46, -117.671,       8L
  )
```




