---
title: "Lecture7a_Markdown"
author: "Amanda"
date: "3/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Libraries
```{r}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
```

Today's Data
```{r}
popdata<-read_csv(here("Week_7", "Data", "CApopdata.csv"))
stars<-read_csv(here("Week_7", "Data", "stars.csv"))
```

map_data("location") is the function used to pull out whaatever base layer that you want
```{r}
# get the data for the world
world<-map_data("world")
head(world)
# get data for the USA
usa<-map_data("usa")
head(usa)
# get data for italy
italy<-map_data("italy")
head(italy)
# get data for states
states<-map_data("state")
head(states)
counties<-map_data("county")
head(counties)
```

*long* is longitude.  
*lat* is latitude  
*order* This just shows in which order ggplot should "connect the dots"  
*regon and subregion* tell what region or subregion a set of points surrounds  
*group* Essentially, having to points in different groups means that ggplot “lifts the pen” when going between them
*Download the data at the highest resolution that you will need*  

Let's make a map of the world
```{r}
ggplot()+
  geom_polygon(data = world, aes(x = long, 
                                 y = lat, 
                                 group = group, 
                                 fill = region),  
                                 color = "black")+
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.background = element_rect(fill = "lightblue"))+
  coord_map(projection = "sinusoidal", 
            xlim = c(-180, 180))
```

Let's make a map of just California
```{r}
# Use the states dataset
head(states)
# Filter out just the California data
CA_data<-states %>%
  filter(region == "california")

ggplot()+
  geom_polygon(data = CA_data, aes(x = long, 
                                 y = lat, 
                                 group = group),  
                                 color = "black")+
               
  guides(fill = FALSE)+
  theme_minimal()+
  theme(panel.background = element_rect(fill = "white"))+
  coord_map(projection = "mercator")

## can also use theme_void() to make a floating map 

```
We are going to plot the population of every county in California

```{r}
# look at the county data
head(counties) [1:3]
head(popdata)

Capop_county<-popdata %>%
  select("subregion" = County, Population) %>%
  inner_join(counties) %>%
  filter(region == "california")

# use the fill function to fill the population by county
ggplot()+
  geom_polygon(data = Capop_county, 
               aes(x = long, 
                   y = lat, 
                   group = group, 
                   fill = Population), 
               color = "black")+
  coord_map()+ 
  theme_void()+
  scale_fill_gradient(trans= "log10")

# look at population of people and sea stars
head(stars)
ggplot()+
  geom_polygon(data = Capop_county, 
               aes(x = long, 
                   y = lat, 
                   group = group, 
                   fill = Population), 
               color = "black")+
  geom_point(data = stars, 
             aes(x = long, 
                 y = lat, 
                 size = star_no))+
  coord_map()+ 
  theme_void()+
  scale_fill_gradient(trans= "log10")+
  labs(size = "# stars/m2")+
  ggsave(here("Week_7", "Output", "CApop_lecture.pdf"))
```

